---
title: "Extension Write Up"
author: "Kate Champion"
date: 12-5-2024
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I extended Gerber et al 2009 by examining heterogeneity in outcome by race. Recall this paper has multiple regression specifications. An OLS regression that measures directly the effect of the party registration mailer on political opinions and behavior. There were two IV specification that used pre-treatment party lean as an instrument, both in absolute and relative terms. I extended this be seeing if there were differential effects for black citizens in the experiment. The new regression specifications are as follows. For the OLS regression: $$Y_{it+1} = \alpha + \beta_{1}T + \beta_{2}Blck + \beta_{3}Blck \mathrm{x} T + \beta_{4}Y_{it}+\beta_{4}D_{it} + \gamma M_{it} + \varepsilon$$
Where i is the individual observed, t and t+1 are the pre-treatment and post-treatment time periods, Y is the outcome of interest, T is a dummy for the treatment group, Blck is a dummy for if an individual is Black or not, Blck x T interacts race with the treatment, D is a dummy for initial partisan lean, and M is a vector of observables. The IV regression is very similar except now it includes the instrument X. 
$$Y_{it+1} = \alpha + \beta_{1}X_{it+1} + \beta_{2}Blck + \beta_{3}Blck \mathrm{x} X_{it+1} + \beta_{4}Y_{it}+\beta_{4}D_{it} + \gamma M_{it} + \varepsilon$$
The results are sensitive to regression specification. The OLS and first IV specification are both positive for the interaction suggesting that Black individuals responded more strongly to the treatment than the other groups (Table 1). However, in the second the IV specification the sign flips, and additionally the magnitude between the OLS and first IV regression is drastically different. This is not surprising because roughly half of the observations had to be dropped due to missing racial information and the ratio of Black individuals to others is very skewed, so the underlying data is very noisy. Therefore, it's hard to say anything conclusive about whether there was a heterogeneous response to the treatment by race. 
```{r print_table}
# Set to the directory to find the saved table_1
# Change everything before econ280project to be your path to the econ280project repo
table_1 <- readRDS("/Users/katechampion/Documents/UCSD/ECON280/econ280project/02_code/table_1.rds")
# Look I tried so hard to get line wraps in this table in nothing worked so sorry it looks stupid
table_1
```


